Gravitational Lens Modelling of Flux Ratio Anomalous System B1555+375

### 2015-04-22 papers/B1555_EdgeOn/B1555_letter.tex
Edits to discussion section

Gravitational lensing is [one of] the most powerful methods for
studying substructure in galaxies outside of the Local Universe, and
the flux ratio anomaly systems are a key aspect of these
investigations.  However, before using the flux ratio anomaly in any
given system to investigate structure formation and the properties of
dark matter, it is critical to eliminate other possible explanations
for the difference between the observed and expected fluxes.  It
is for this reason that much of the effort in the flux-ratio technique
has been focused on radio-loud lens systems.  At these wavelengths,
dust extinction and microlensing effects should be minimal (although
see \citet{K2000} for a rare example of radio microlensing).
Radio propagation effects can  affect radio fluxes, as is clearly
shown in the B0128 system \citep{B04}.  However, these propagation effects
can be disentangled from substructure lensing because they have well
known dependencies on wavelength. \citet{KD04} examine all eight radio loud flux anomalous lenses: MG 0414+0534, B0712+472,  B1359+154, B1422+231, B1555+375, B1608+656, B1933+503, and B2045+265. 
They find no strong wavelength dependence in the flux ratios of all these systems and rule out the possible affects from radio propagation.

In our models based on the new imaging from the SHARP $K^{\prime}$
band observations, the most significant difference in comparison to
previous modelling is a new edge-on disk component. With a bulge plus
an edge-on disk, our models produce matches to both the radio image
positions and the flux ratio, while models with only one SIE
component \citep{Marlow,Xu14} fail to reproduce the fluxes
correctly. Our successful modelling indicates that the
kiloparsec-scale structure of lens galaxy itself is sufficient to
explain the flux ratio anomalies in B1555+375, without any need to
invoke the presense of substructrue. This breaks the idea that in
strongly lensed quasars, radio flux ratio anomalies are most likely
originated from substructure perturbations. Our discovery shows a complex lens galaxy mass
distribution can dominate flux ratio anomalous phenomena in a strongly
lensed system.

From theoretical perspective, \citet{Xu14}  find that substructures cannot expalin radio flux anomalies in all these lenses. By adding subhaloes from numerical simulations on to these systems, only one out of eight radio loud systems reproduces the flux anomalies. The rest of them are unlikely (only $1 \% - 4 \%$ probability) to have substructure originated flux anomalies, including our target B1555+375. Among those eight radio lenses, B1555+375 is one of the most anomalous systems, but it is also one of the most challenging systems to explain by substructures. \citet{Xu14} conclude the failure in predicting flux ratios is due to oversimplified/improper lens modelling. They also outline that the SIE component and the external shear are orthogonal indicates a possible missing ingredient in lens model. Their results are consistent with the SHARP $K^{\prime}$ band observations, which an edge-on disk lies cross the radio merging double in B1555+375. B1555+375 is not the only system having edge-on disk detection in SHARP near-infrared AO imaging (see Fig 4). We would like to draw attention to the possible impacts on substructure searching from this enge-on disk orginated flux anomalies. It is a sign that researchers should be careful about the flux anomalies fraction in lensed quasars. It may be worth considering an upper limit of flux anomalies fraciton from observation results to avoid over estimate the number of substructure detections. Although the number of radio loud flux anomalous lensed quasars remains small, a new technique using narrow-line emissions will enlarge the sample and bring statistical perspective on substructures in the near future \citep{N14}. For further analysis on substurcture population, mass function etc., it is always important to rule out other non-substructure effects.

In this paper we also demostrate the power of combining multiwavelength high resolution data. All the flux anomalous lensed quasars are radio loud systems and are first discovered in radio observations. Radio data provides reliable information on positions and fluxes of lensed images but often unable to detect lens galaxies. Since lens galaxies are mostly in low redshift, optical and near-infrared observations are ideal to measure the light distribution of lens gaxies and obtain prior on underlying mass distribution. In the previous paper of SHARP, \citet{SHARP12} show that high resolution IR imaging can help to improve lens modelling. The improvement is even more dramatic in B1555+375. With HST and SHARP AO high resolution imaging, we detect an edge-on disk which does not appear in any previous discussions on B1555+375. This new discovered edge-on disk provides a strong hint to our lens modelling and we show that it adequately explain sthe flux ratio anomaly in B1555+375. Our results demostrate that lack of knowledge of lens galaxies can lead to improper lens models. Modelling with only four image positions from radio data can also cause a lot of degeneracy. With the first system analyzing and finding an edge-on disk originated flux ratio anomaly, our follow up will be explore other similar SHARP systems. In Figure 3, all of these systems have a recognizable edge-on disk in infrared imaging. An edge-on disk structure may also be able to expalin the flux ratio anomalies of these systems.\\

>>>>

Gravitational lensing is [one of] the most powerful methods for
studying substructure in galaxies outside of the Local Universe, and
the flux ratio anomaly systems are a key aspect of these
investigations.  However, before using the flux ratio anomaly in any
given system to investigate structure formation and the properties of
dark matter, it is critical to eliminate other possible explanations
for the difference between the observed and expected fluxes.  It is
for this reason that much of the effort in the flux-ratio technique
has been focused on radio-loud lens systems.  At these wavelengths,
dust extinction and microlensing effects should be minimal
\citep[although see][for a rare example of radio microlensing]{K2000}.
Radio propagation effects can affect radio fluxes, as is clearly shown
in the B0128+437 system \citep{B04}.  However, these propagation
effects can be disentangled from substructure lensing because they
have well known dependencies on wavelength. \citet{KD04} examine all
eight radio loud flux anomalous lenses besides B0128=437, namely: MG
0414+0534, B0712+472, B1359+154, B1422+231, B1555+375, B1608+656,
B1933+503, and B2045+265.  They find no strong wavelength dependence
in the flux ratios of all these systems and therefore rule out radio
propagation effects as significant contributors to the observed
anomalies.

In our models based on the new imaging from the SHARP $K^{\prime}$
band observations, the most significant difference in comparison to
previous modelling is a new edge-on disk component. With a bulge plus
an edge-on disk, our models produce matches to both the radio image
positions and the flux ratio, while models with only one SIE
component \citep{Marlow,Xu14} fail to reproduce the fluxes
correctly. Our successful modelling indicates that the
kiloparsec-scale structure of lens galaxy itself is sufficient to
explain the flux ratio anomalies in B1555+375, without any need to
invoke the presense of substructure.

% This breaks the idea that in strongly lensed quasars, radio flux ratio
% anomalies are most likely originated from substructure
% perturbations. Our discovery shows a complex lens galaxy mass
% distribution can dominate flux ratio anomalous phenomena in a strongly
% lensed system.

From a theoretical perspective, \citet{Xu14} find that substructures
cannot explain the observed radio flux anomalies in all the lenses
that were considered. By adding subhaloes from numerical simulations
on to these systems, only one out of eight radio loud systems
reproduces the level of flux anomalies seen in the data.  The rest of
them are unlikely (only $1 \% - 4 \%$ probability) to have flux
anomalies produced by substructure, including our target B1555+375.
In fact, among those eight radio lenses, B1555+375 is one of the most
anomalous systems, but it is also one of the most challenging systems
to explain by substructures. \citet{Xu14} conclude the failure in
predicting flux ratios is due to oversimplified/improper lens
modelling. They also point out that the SIE component and the external
shear in their model are orthogonal, indicating a possible missing
ingredient in lens model. Their results are consistent with the SHARP
$K^{\prime}$ band observations, in which an edge-on disk crosses the
radio merging double.

Additional near-infrared AO imaging from SHARP shows that B1555+375 is
not the only system having a significant disk component detection in
the lensing galaxy (see Fig 4).  These systems will be investigated in
future work, but the images alone strongly suggest that other lens
systems have similar links between flux-ratio anomalies and disk
components.  Although the number of radio loud flux anomalous lensed
quasars remains small, a new technique using narrow-line emission
regions will enlarge the sample and bring statistical perspective on
substructures in the near future \citep{N14}. It is well known (e.g,
Kochanek 199??) that lens models based only on the locations of lensed
quasar/AGN images have large degeneracies.  Therefore, before
concluding that the flux ratios in any given lens system are a result
of substructure, it is critical to explore a range of smooth models
that are informed by additional observations or to do a comprehensive
analysis such as that conducted by \citet{Xu14}.  Otherwise, derived
substructure fractions should be considered as upper limits.

% We would like to draw attention to the possible impacts on
% substructure searching from this enge-on disk orginated flux
% anomalies. It is a sign that researchers should be careful about the
% flux anomalies fraction in lensed quasars. It may be worth considering
% an upper limit of flux anomalies fraciton from observation results to
% avoid over estimate the number of substructure detections. For further
% analysis on substurcture population, mass function etc., it is always
% important to rule out other non-substructure effects.

[PERHAPS REARRANGE THE FOLLOWING INTO A CONCLUSIONS SECTION??]

In this paper we also demostrate the power of combining multiwavelength high resolution data. All the flux anomalous lensed quasars are radio loud systems and are first discovered in radio observations. Radio data provides reliable information on positions and fluxes of lensed images but often unable to detect lens galaxies. Since lens galaxies are mostly in low redshift, optical and near-infrared observations are ideal to measure the light distribution of lens gaxies and obtain prior on underlying mass distribution. In the previous paper of SHARP, \citet{SHARP12} show that high resolution IR imaging can help to improve lens modelling. The improvement is even more dramatic in B1555+375. With HST and SHARP AO high resolution imaging, we detect an edge-on disk which does not appear in any previous discussions on B1555+375. This new discovered edge-on disk provides a strong prior for our lens modelling and we show that it adequately explain sthe flux ratio anomaly in B1555+375. Our results demostrate that lack of knowledge of lens galaxies can lead to improper lens models. Modelling with only four image positions from radio data can also cause a lot of degeneracy. With the first system analyzing and finding an edge-on disk originated flux ratio anomaly, our follow up will be explore other similar SHARP systems. In Figure 3, all of these systems have a recognizable edge-on disk in infrared imaging. An edge-on disk structure may also be able to expalin the flux ratio anomalies of these systems.
